### 2020-01-20 ChapterProblemDefinition/chapterProblemDefinition.tex
Updated: Explanation of time-space inconsistencies and explanation of why end state can't be used to measure correctness

%TODO: Describe physics errors in detail here
%Late collisions
%Things not colliding (i.e. overlapping when they shouldn't be)
%Objects not being simulated
%Objects jittering

@@

\subsection{Time-space inconsistencies}
%Objects being simulated on different servers may end up occupying the same space.
%If a solution is used in which 
%Objects may be unaware of objects on a different server

\subsection{Diverging results}\label{divergingResults}
PhysX is non-deterministic, as a result of this, repeating the same scenario with the exact same starting parameters does not necessarily lead to the exact same end state.
If collision response is performed on different servers with the same group of objects, they will not lead to the same results. PhysX has an option for increased determinism, but as servers will have different states, as they will be hosting objects that the other server is not, this will not guarantee the exact same results.
The results of a single differing collision response can create a significantly different state of objects, for example if a stack of cubes is dropped onto a flat level plane, the cubes land is such a way where the stack is on the verge of collapsing. In one iteration, the stack of cubes may remain standing, in a second iteration, the stack of cubes may collapse.

>>>>

@@

\subsection{Time-space inconsistencies}
Objects being simulated on different servers may end up occupying the same space and the same time, which is a physical inconsistency. This error could occur due to latency issues between servers or if a naive approach is taken to handling objects near server-region boundaries. For example, in a naive approach, object ownership may be determined by the centre of the object and no special consideration is given to objects near server-region boundaries. If two objects on different servers are overlapping the boundary at the same place, but their centres remain in their owning server's region, the two objects will have no interaction, despite occupying the same space at the same time. In a centralised version of the simulation, the two objects would collide and interact as soon as the two began to overlap with each other.
%If a solution is used in which 
%Objects may be unaware of objects on a different server

\subsection{Diverging results}\label{divergingResults}
PhysX is non-deterministic, as a result of this, repeating the same scenario with the exact same starting parameters does not necessarily lead to the exact same end state. The order in which collisions are resolved are randomised to achieve greater stability of the simulation.
If collision response is performed on different servers with the same group of objects, they will not lead to the same results. PhysX has an option for increased determinism, but as servers will have different states, as they will be hosting objects that the other server is not, this will not guarantee the exact same results. The results of a single differing collision response can create a significantly different state of objects, for example if a stack of cubes is dropped onto a flat level plane, the cubes land is such a way where the stack is on the verge of collapsing. In one iteration, the stack of cubes may remain standing, in a second iteration, the stack of cubes may collapse.

As a consequence of non-determinism and diverging results, it is not possible to measure correctness of a distributed simulation by comparing it with a single centralised simulation, i.e. run both solutions with the exact same starting parameters and compare the final state of the distributed simulation to the centralised simulation. A distributed solution can produce a significantly different final state compared to a centralised solution, despite handling all collisions correctly.
